---
title: "publR package"
author: "Daniel Hammarström"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{publR package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## The publR package

The publR package is built to contain functions that makes it easier to write reports in R. To date there are thre functions in the package, they will be covered here. 

### `publr_color`
`publr_color()` contaions a selection of palettes to be used for plotting. All palettes has been selected to be color-blind friendly. Some are photo-copy and printer-friendly too. 

To get an overview of the palettes, one can simply choose to display all the palettes using set the `display = TRUE`.
```{r publr_color}
library(ggplot2); library(publR)
publr_color(display = TRUE)

```

To select a palette from the function, simply give the name of the palette to the function, e.g:

```{r publr_color select colors}

publr_color("cxxs19")

```

One can also subset the function to get a selection of colors from the specified palette.

```{r publr_color select subset colors}

publr_color("cxxs19")[c(1,3)]

```

To use the palette in a ggplot, use e.g. `scale_fill_manual` and specify the values with `publr_color`:


```{r publr_color in plot}

data(iris)

ggplot(iris, aes(Sepal.Width, Sepal.Length, fill = Species)) + geom_point(size = 4, shape = 21) +
        scale_fill_manual(values=publr_color("cxxd05")[c(3,7,11)])


```

### `publr_theme`

The `publr_theme` is a low-key theme to start with when preparing figures for publication. Here you can modify theme components using:

* `font_family`
* `axis_line_width` 
* `font_size_labels` 
* `font_size_axis` 
* `text_color`

```{r publr_theme}

data(iris)

ggplot(iris, aes(Sepal.Width, Sepal.Length, fill = Species)) + geom_point(size = 4, shape = 21) +
        scale_fill_manual(values=publr_color("cxxd05")[c(3,7,11)]) +
        publr_theme(font_family = "mono", axis_line_width = 0.5, font_size_labels = 10, font_size_axis = 8,
                    text_color = "black")


```


### `pval`
The `pval` function makes it easy to flag or truncate p-values in text and in plots. When `pval` is used in `annotate`, use `parse=TRUE` to print the p-value.

```{r}


p <- cor.test(iris$Sepal.Width, iris$Petal.Length)$p.value

ggplot(iris, aes(Sepal.Width, Sepal.Length, fill = Species)) + geom_point(size = 4, shape = 21) +
        scale_fill_manual(values=publr_color("cxxd05")[c(3,7,11)]) +
        publr_theme(font_family = "mono", axis_line_width = 0.5, font_size_labels = 10, font_size_axis = 8,
                    text_color = "black") +
        annotate("text", x= 4, y = 7.5, label = pval(p, plot = TRUE), parse = TRUE, size = 2)

```


When using the `pval` in the text, set plot to FALSE. E.g. a p-value of `0.0002345` can be truncated and printed to `r pval(0.0002345, plot = FALSE)` using `pval(0.0002345, plot = FALSE)`. The function gives an exact p-value when the p-value is above the digits threshold, e.g. if digits are = 3, the threshold is 0.001, p-values above this threshold prints to the closest significant number. 

The function can also flag significances using the argument `flag=TRUE`, the function gives &ast; for p-values 0.01-0.05; &ast;&ast; for 0.001-0.01; &ast;&ast;&ast; for 0.001-0.0001; &ast;&ast;&ast;&ast; for 0-0.0001.

